Conditions for $d$-local-connectedness of boundaries of hyperbolic groups

### 2020-02-10 paper.tex
Proved taht simply connected implies S

In this section we give a sufficient condition for our condition
\todo{condition} to be satisfied.

>>>>

In this section we give a sufficient condition for the condition $\S_M$ to be
satisfied.

\begin{proposition}
  Suppose that $\boundary G - \set\xi$ is simply connected for any point $\xi
  \in \boundary G$. Then $\S_M$ is satisfied for all $M$.
\end{proposition}

\begin{proof}
  Suppose that the condition is not satisfied. Then for each $i$ there exists a
  number $n_i \geq i$, a map $\gamma_i \from \boundary\Delta \to \boundary G$
  and a simplicial map $f_i \from \sd^M \boundary\Delta \to K_{n_i}$ that is a
  simplicial approimxation to $p^\infty_{n_i}\composed\gamma_i$ such that $f_i$
  does not admit an extension to $\Delta$ that is affine on $\sd^i\Delta$.

  Fix a vertex $v$ of $\boundary\Delta$; then there exist group elements $g_i
  \in G$ such that $g_i\cdot f_i(v)$ is a fixed vertex of $K$. Pass to a
  subsequence as in Section~\ref{sec:horoball}, and to a deeper subsequence so
  that $g_i\cdot f_i(w)$ is independent of $i$ for all vertices $w \in \sd^M
  \boundary\Delta$. Then the map $g_i\composed f_i$ is independent of $i$; call
  this map $f$. It remains to show that $f$ is nullhomotopic in $H$; then it is
  nullhomotopic by a simplicial map, and this gives a contradiction for $i$
  sufficiently large.

  By Lemma~\ref{lem:propermaps} there exists $i_0$ and a 
  compact set $C_0 \subset \boundary G - \set\xi$ such that $C_0$ contains the
  image of $\gamma_i$ for every $i \geq i_0$. By
  Lemma~\ref{lem:affinehomotopic} there exists $i_1 \geq i_0$ such that
  $q_i\restricted{C_0}$ is affine homotopic to $q_{i_1}\restricted{C_0}$ for
  every $i \geq i_1$.

  Let $h$ be a nullhomotopy of $\gamma_{i_1}$ in
  $\boundary G - \set\xi$ and let $C_1$ be a compact subset of $\boundary G -
  \set\xi$ containing $C_0$ and the image of $h$. Let $i_2$ be so that $C_1
  \subset U_{i_2}$.

  Then $f$ is homotopic to $q_{i_1}\composed\gamma_{i_1}$, which is homotopic
  to $q_{i_2}\composed\gamma_{i_1}$, which is homotopic by $q_{i_2}\composed h$
  to a point.
  \todo{would just $i_0$ and $i_1$ have been enough?}
\end{proof}
